Supplemental Appendix: Penalized regression for left-truncated and right-censored survival data

### 2021-01-08 supplement.tex
Update to Figure S2 in Supplement

\begin{figure}[h]
\centering
\includegraphics[max size={\textwidth}]{figs/sim_int_km_plot_rwd_v_sim.pdf} 
\caption{Kaplan-Meier plots of overall survival from models that adjust for right censoring but not left truncation in the simulated data and CGDB}
\begin{minipage}{\linewidth}
\footnotesize
Notes: The simulated dataset was simulated using an intercept only Weibull model with no predictors. Only non-truncated patients from the simulation were used for estimation. 
\end{minipage}
\end{figure}

>>>>

\begin{figure}[h]
\centering
\includegraphics[max size={\textwidth}]{figs/sim_p11_km_plot_rwd_v_sim.pdf} 
\caption{Kaplan-Meier plots of overall survival from models that adjust for right censoring but not left truncation in the simulated data and CGDB}
\begin{minipage}{\linewidth}
\footnotesize
Notes: The simulated dataset was simulated using a Weibull model including the predictors described in the main text from the CGDB. Only non-truncated patients from the simulation were used for estimation. 
\end{minipage}
\end{figure}
